Methods for Projecting Population Growth

### 2018-05-08 final/tex/Paper.tex
Update captions

\todo{Fix figure captions}

\todo{Add figure labels/references}

@@

@@

\begin{figure}[ht!]
\includegraphics[width=80mm]{images/world-pop.png}
\includegraphics[width=80mm]{images/world-gdp.png}
\caption{Results of modeling world population and GDP by manual modifications based off of minimizing scoring function \label{overflow}}
\end{figure}

@@

\begin{figure}[ht!]
\includegraphics[width=80mm]{images/us-pop.png}
\includegraphics[width=80mm]{images/us-gdp.png}
\caption{Results of modeling U.S. population and GDP by using the least squares method\label{overflow}}
\end{figure}

@@

@@

\begin{figure}[ht!]
\includegraphics[width=80mm]{images/sa-pop.png}
\includegraphics[width=80mm]{images/sa-gdp.png}
\caption{Results of modeling South Africa population and GDP by using the least square method.  \label{overflow}}
\end{figure}

>>>>

@@

\begin{figure}[t!]
\includegraphics[width=80mm]{images/world-pop.png}
\includegraphics[width=80mm]{images/world-gdp.png}
\caption{World population and GDP modeled with parameters  $\alpha_1 = 0.3\%$, $\alpha_3 k_1 = \frac{5.2}{10^{6}}\frac{Hab.}{US \$}$, $\alpha_2 = \frac{-55}{10^{17} US\$}$, $\beta_1 = 3.6\%$, and $\beta_2 = \frac{-2}{10^{22} Hab.}$ against logistic-growth with parameters  $\gamma = 2.72\%$, $K = 12,263,457,578 $ Hab. \label{overflow}}
\end{figure}

@@

@@

@@

\begin{figure}[t]
\includegraphics[width=80mm]{images/us-pop.png}
\includegraphics[width=80mm]{images/us-gdp.png}
\caption{U.S. population and GDP modeled with parameters   $\alpha_1 = 1.07\%$, $\alpha_3 k_1 = \frac{2.76}{10^{7}}\frac{Hab.}{US \$}$, $\alpha_2 = \frac{-1.04}{10^{15} US\$}$, $\beta_1 = 17.9\%$, and $\beta_2 = \frac{-4.63}{10^{10} Hab.}$ against logistic-growth with parameters  $\gamma = 1.71\%$, $K = 632,260,032$ Hab.\label{overflow}}
\end{figure}

@@

\begin{figure}[t!]
\includegraphics[width=80mm]{images/sa-pop.png}
\includegraphics[width=80mm]{images/sa-gdp.png}
\caption{South Africa population and GDP modeled with parameters $\alpha_1 = 2.22\%$, $\alpha_3 k_1 = \frac{2.77}{10^{6}}\frac{Hab.}{US \$}$, $\alpha_2 = \frac{-8.31}{10^{14} US\$}$, $\beta_1 = 29.0\%$, and $\beta_2 = \frac{-5.21}{10^{9} Hab.}$ against logistic-growth with parameters   $\gamma = 3.85\%$, $K = 79,007,800$ Hab. \label{overflow}}
\end{figure}
